Polyglots: Crossing Origins by Crossing Formats

### 2013-08-26 main.tex
no message

\begin{abstract}
 In a heterogeneous system like the web, information is
exchanged between components in versatile formats. A new breed of attacks is on
the rise that exploit the mismatch between the expected and provided content.
% 
This paper identifies the root cause of a large class of attacks: \emph{polyglots}. 
A polyglot is a program that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
%
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. 
%
The paper presents novel attack vectors that infiltrate the trusted
origin by \emph{syntax injection} across multiple languages and by
\emph{content smuggling} of
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
  request forgery}.
%
We perform a systematic study of
PDF-based injection and content smuggling attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web
sites.
%
We identify five web sites to be vulnerable to syntax injection
attacks. Further,
%
we have found two major
enterprise cloud storage services to be susceptible to content
smuggling attacks.
%
Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (in particular, PDF readers) show how to mitigate the attacks.
\end{abstract}

@@

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
An attacker can use a malicious polyglot to infiltrate a vulnerable origin.
Once infiltrated, the polyglot is embedded from within the attacker's web site,
such that the browser is coerced to interpret the polyglot in an unexpected context, e.g., a plug-in.
According to the SOP, content loaded in a plug-in is considered to belong to the 
origin from which the content was requested. Thus, the polyglot is allowed to communicate with the vulnerable 
origin. A victim, authenticated in the vulnerable origin, who visits the attacker's web site
will trigger the malicious polyglot. This allows the polyglot to abuse the credentials of the victim 
in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
where we present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\paragraph{Generalizing polyglot attacks} 
The paper is the first to perform a generalization and systematic study of polyglot
attacks.
We identify the necessary ingredients for polyglot attacks.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins.

@@

%3 pages
\section{Crossing origins by crossing formats}
\label{sec:cross}
% Describe how the attacks lead to same-origin policy bypass.

This section describes how formats can be crossed and how that can be abused 
to cross origins by circumventing the same-origin policy. We begin by 
describing cross-origin information leaks, next we
generalize the problem of crossing formats to \emph{polyglots} and describe the  
characteristics of a malicious polyglot. From that we derive two attack vectors and 
show how previous work on the subject relate to these vectors.

@@

Other examples of problematic elements include the \emph{object} and
\emph{embed} tags. These 
tags allow inclusion of resources that may require a 
plug-in to run. The plug-in is selected based on the MIME-type of the content, but
because the server delivering the content might not be able to determine its
format, the tags allow a developer to set the type attribute to guide the
browser in which plug-in to run. When the type attribute is used, the
corresponding plug-in is run regardless of the MIME-type provided by the server. 
%
In the event that the provided MIME-type do not match that for which the plug-in is 
designed, e.g., \emph{text/html} for a PDF plug-in, it is up to the plug-in to respond to the content it is served.
Known methods of handling MIME-types, such as content-sniffing, are effective 
in this situation, but they have to be employed by each and every plug-in.
Most plug-ins will disregard the MIME-type of the content and attempt to parse 
it. 
%
As with images, the content handled by the plug-in is executed in the origin it was served from. 
This implies that the containing page is restricted 
from directly accessing the content handled by the plug-in, and that the content can 
communicate freely with the origin it was loaded from. However,  a number of plug-ins provide 
an API for interaction between the plug-in and the document.
The browsers are forced to rely on the plug-ins to employ correct security 
measures. Section~\ref{sec:eval} shows that even state-of-the-art plug-ins fail to 
properly do so, emphasizing the importance of increasing awareness on the issue. 
%Next we show how crossing formats
%to cross-origin information leaks.

@@

Coercing content to be interpreted
as a different type can be accommodated in the context of the web. 
If the content is loaded using an \emph{image} tag it will be interpreted 
as an image, if a \emph{script} tag is used it will be interpreted as a script. Certain
tags, e.g., the object-tag and embed-tag, even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues. 
%

Barth et al.~\cite{Barth+:SP09} define \emph{chameleon} documents 
as a benign file type crossbred with malicious HTML content. The attack 
targets the content-sniffing algorithm used in the browser and the document 
is crafted in such a way that the browser 
will detect the content type as HTML. The paper proceeds to 
describe how an attacker can create a 
\emph{chameleon} document, that is valid PostScript, but will be identified as HTML.
This issue allows exploitation when there is a mismatch between a web site's 
content validation filter and the browsers content-sniffing algorithm.

@@

While these articles document known instances of polyglot attacks, the attack 
method has not been generalized until this paper.
%
Under our generalization, previous work corresponds to
instances. For example, we show that GIFAR attacks describe a form of content smuggling, Section~\ref{sec:smuggling}, and
cross-origin CSS attacks~\cite{Huang+:CCS10} describe a form of syntax injection attacks, Section~\ref{sec:injection}.
%
The added value of our paper is a generalized view and focus on new
instances of polyglots that involve the PDF format.

@@

This paper identifies two vectors for infiltrating an origin, either via syntax 
injection, or content smuggling. In the case of syntax injection, existing content is manipulated
to become a polyglot, whereas with content smuggling, a polyglot is used to evade 
content filters. The vectors are described below with more detailed scenarios.

@@

Not only in-line JavaScript fall short in this regard. JavaScript object notation 
(JSON) is used in modern web sites as a data transport. This is particularly 
common in web sites that provide an API to interact with the offered services.
JSON encoded information suffer the same problem as in-line JavaScript, thereby
extending the attack surface further.

@@

\paragraph{Internet Explorer}
Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
it seems to only support embedding of PDF documents using the \emph{embed} tag. 
This is not a major obstacle in exploiting the vulnerability, as the embed and 
object tags are interchangeable in this respect.

@@

Note that although some of the mitigation suggestions discussed below are already in place
(notably as implemented by the Chrome builtin PDF reader), the state of the art
is far from being satisfactory. As our paper demonstrates, the
polyglot attacks are a real threat. It is the paper's main value to
bring attention to polyglot attacks and the importance of
mitigation against them.

@@

The relation between web server and the browser is central in a web environment, but 
there is no common agreement on the type of content communicated between server 
and client. As mentioned in Section~\ref{sec:cross-origin}, in each response the web server sends a 
header representing its view on the type of content delivered, however, the browser
is free to ignore the provided type and can even be instructed to do so.
Often the browser knows precisely the context in which the content will be 
rendered and the types suitable for these contexts. 
%
As an example, when content is loaded in an object-tag with a type attribute, as 
is the case throughout the paper, the browser already
has exact knowledge as to which types the requested content can be interpreted as in this context. A natural
defense technique is to send the expected types along with the request. The web server
then compares the expected types to the assumed type and react accordingly, e.g., 
if the assumed type is HTML and the expected type is PDF, an 
error can be sent back to the client. On the client side, the browser verifies 
the type in the response matches any of the expected types, possibly alerting 
the user if there is a mismatch. This mutual agreement between client and server
can help mitigate both syntax injection and content smuggling.
Furthermore, this approach can be implemented in the
web server itself, as opposed to a web application, since the web server makes the
final decision on the supplied content-type.

@@

There are limitations to this technique; If a context has multiple possible types, e.g., an image-tag, 
a polyglot between two of the types can evade detection. The specific cases where this situation 
occurs in an exploitable way are rare, and further work can help in determining and mitigating such 
vulnerabilities.

@@

Preventing syntax injection attacks on the server-side poses severe challenges.
Even server-side filtering of HTML syntax to prevent cross-side scripting
attacks has proved difficult due to the many contexts in which JavaScript can be 
introduced. Filtering all potentially harmful tokens from all formats in which a 
document may be interpreted is hardly possible.

@@

%1 page 
\section{Related work}
\label{sec:related}
Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
language. PostScript allows executable content and access to sensitive
information from the environment such as the user id. This work
demonstrates how to compromise reviewer anonymity in a peer-reviewing
process by maliciously crafting a PostScript document.

@@

Barth et al.~\cite{Barth+:SP09} focus on security implications of
content sniffing by browsers. They present content-sniffing XSS
attacks by crossbreeding HTML with other formats like PostScript. They
show attacks on real systems like HotCRP, where an uploaded conference
paper in the PostScript format is interpreted as malicious HTML by the
browser. They also propose a content-sniffing algorithm that does not
suffer that helps defending against these class of attacks while
maintaining compatibility.

>>>>

\begin{abstract}
 In a heterogeneous system like the web, information is
exchanged between components in versatile formats. A new breed of attacks is on
the rise that exploit the mismatch between the expected and provided content.
% 
This paper focuses on the root cause of a large class of attacks: \emph{polyglots}. 
A polyglot is a program that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
%
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. 
%
The paper presents novel attack vectors that infiltrate the trusted
origin by \emph{syntax injection} across multiple languages and by
\emph{content smuggling} of
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
  request forgery}.
%
We perform a systematic study of
PDF-based injection and content smuggling attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web
sites.
%
We identify five web sites to be vulnerable to syntax injection
attacks. Further,
%
we have found two major
enterprise cloud storage services to be susceptible to content
smuggling attacks.
%
Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (in particular, PDF readers) show how to mitigate the attacks.
\end{abstract}

@@

\paragraph{Crossing origins by crossing formats}
This paper focuses on a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
An attacker can use a malicious polyglot to infiltrate a vulnerable origin.
Once infiltrated, the polyglot is embedded from within the attacker's web site,
such that the browser is coerced to interpret the polyglot in an unexpected context, e.g., a plug-in.
According to the SOP, content loaded in a plug-in is considered to belong to the 
origin from which the content was requested. Thus, the polyglot is allowed to communicate with the vulnerable 
origin. A victim, authenticated in the vulnerable origin, who visits the attacker's web site
will trigger the malicious polyglot. This allows the polyglot to abuse the credentials of the victim 
in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
where we present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\paragraph{Generalizing polyglot attacks} 
The paper is the first to present a generalized description of polyglot
attacks.
We identify the necessary ingredients for polyglot attacks.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins.

@@

%3 pages
\section{Crossing origins and formats}
\label{sec:cross}
% Describe how the attacks lead to same-origin policy bypass.

This section describes how formats can be crossed and how that can be abused 
to cross origins by circumventing the same-origin policy. We
describe cross-origin information leaks,
generalize the problem of crossing formats to \emph{polyglots}, and present the  
characteristics of a malicious polyglot. From that we derive two attack vectors and 
show how previous work on the subject relate to these vectors.

@@

Other examples of problematic elements include the \emph{object} and
\emph{embed} tags. These 
tags allow inclusion of resources that may require a 
plug-in to run. The plug-in is selected based on the MIME-type of the content, but
because the server delivering the content might not be able to determine its
format, the tags allow a developer to set the type attribute to guide the
browser in which plug-in to run. When the type attribute is used, the
corresponding plug-in is run regardless of the MIME-type provided by the server. 
%
In the event that the provided MIME-type do not match that for which the plug-in is 
designed, e.g., \emph{text/html} for a PDF plug-in, it is up to the plug-in to respond to the content it is served.
Known methods of handling MIME-types, such as content-sniffing, are effective 
in this situation, but they have to be employed by each and every plug-in.
Most plug-ins will disregard the MIME-type of the content and attempt to parse 
it. 
%
As with images, the content handled by the plug-in is executed in the origin it was served from. 
This implies that the containing page is restricted 
from directly accessing the content handled by the plug-in, and that the content can 
communicate freely with the origin it was loaded from. However,  a number of plug-ins provide 
an API for interaction between the plug-in and the document.
The browsers are forced to rely on the plug-ins to employ correct security 
measures. Section~\ref{sec:eval} shows that even state-of-the-art plug-ins fail to 
properly do so, emphasizing the importance of the issue. 
%Next we show how crossing formats
%to cross-origin information leaks.

@@

Coercing content to be interpreted
as a different type can be accommodated in the context of the web. 
If the content is loaded using an \emph{img} tag it will be interpreted 
as an image, if a \emph{script} tag is used it will be interpreted as a script. Certain
tags, e.g., the \emph{object} tag and \emph{embed} tag, even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues, as illustrated below.
%

Barth et al.~\cite{Barth+:SP09} define \emph{chameleon} documents 
as a benign file type crossbred with malicious HTML content. The attack 
targets the content-sniffing algorithm used in the browser and the document 
is crafted in such a way that the browser 
will detect the content type as HTML. The paper proceeds to 
describe how an attacker can create a 
chameleon document, that is valid PostScript, but will be identified as HTML.
This issue allows exploitation when there is a mismatch between a web site's 
content validation filter and the browser's content-sniffing algorithm.

@@

While these articles document known instances of polyglot attacks, the attack 
method has not been generalized until this paper.
%
Under our generalization, previous work corresponds to
instances. For example, we show that GIFAR attacks describe a form of content smuggling, Section~\ref{sec:smuggling}, and
cross-origin CSS attacks~\cite{Huang+:CCS10} describe a form of syntax injection attacks, Section~\ref{sec:injection}.
%
The added value of our paper is a generalized view on polyglot attacks and focus on new
instances of polyglots that involve the PDF format.

@@

This paper describes two vectors for infiltrating an origin, either via syntax 
injection, or content smuggling. In the case of syntax injection, existing content is manipulated
to become a polyglot, whereas with content smuggling, a polyglot is used to evade 
content filters. The vectors are described below with more detailed scenarios.

@@

Note that not only in-line JavaScript falls short in this regard. JavaScript object notation 
(JSON) is used in modern web sites as a data transport. This is particularly 
common in web sites that provide an API to interact with the offered services.
JSON encoded information suffer the same problem as in-line JavaScript, thereby
extending the attack surface further.

@@

\paragraph{Internet Explorer}
Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
it seems to only support embedding of PDF documents using the \emph{embed} tag. 
This is not a major obstacle in exploiting the vulnerability, as the \emph{embed} and 
\emph{object} tags are interchangeable in this respect.

@@

Although some of the mitigation suggestions below are already in place
(e.g., the Chrome builtin PDF reader), the state of the art
is far from being satisfactory. As our paper demonstrates, the
polyglot attacks are a real threat. It is the paper's main value to
bring attention to polyglot attacks and the importance of
mitigation against them.

@@

The relation between web server and the browser is central in a web environment, but 
there is no common agreement on the type of content communicated between server 
and client. As mentioned in Section~\ref{sec:cross-origin}, in each response the web server sends a 
header representing its view on the type of content delivered, however, the browser
is free to ignore the provided type and can even be instructed to do so.
Often the browser knows precisely the context in which the content will be 
rendered and the types suitable for these contexts. 
%
As an example, when content is loaded in an \emph{object} tag with a type attribute, as 
is the case throughout the paper, the browser already
has exact knowledge as to which types the requested content can be interpreted as in this context. A natural
defense technique is to send the expected types along with the request. The web server
then compares the expected types to the assumed type and react accordingly, e.g., 
if the assumed type is HTML and the expected type is PDF, an 
error can be sent back to the client. On the client side, the browser verifies 
the type in the response matches any of the expected types, possibly alerting 
the user if there is a mismatch. This mutual agreement between client and server
can help mitigate both syntax injection and content smuggling.
Furthermore, this approach can be implemented in the
web server itself, as opposed to a web application, since the web server makes the
final decision on the supplied content-type.

@@

There are limitations to this technique; If a context has multiple
possible types, e.g., an \emph{img} tag, 
a polyglot between two of the types can evade detection. The specific cases where this situation 
occurs in an exploitable way are rare, and further work can help in determining and mitigating such 
vulnerabilities.

@@

Preventing syntax injection on the server-side poses severe challenges.
Even server-side filtering of HTML syntax to prevent cross-side scripting
attacks has proved difficult due to the many contexts in which JavaScript can be 
introduced. Filtering all potentially harmful tokens from all formats in which a 
document may be interpreted is hardly possible.

@@

%1 page 
\section{Related work}
\label{sec:related}
Recall that the added value of our paper is a generalized account of polyglot attacks and focus on new
instances of polyglots that involve the PDF format. We briefly report
on related instances of polyglot attacks.

Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
language. PostScript allows executable content and access to sensitive
information from the environment such as the user id. This work
demonstrates how to compromise reviewer anonymity in a peer-reviewing
process by maliciously crafting a PostScript document.

@@

Barth et al.~\cite{Barth+:SP09} investigate the security implications of
content sniffing by browsers. They present content-sniffing XSS
attacks by crossbreeding HTML with other formats like PostScript. They
show attacks on real systems like HotCRP, where an uploaded document
in the PostScript format is interpreted as malicious HTML by the
browser. They also propose a content-sniffing algorithm
that helps defending against this class of attacks while
maintaining compatibility.
